### 2012-02-11 GUIErrorDetector/paper/introduction.tex
Spacing hacks

\vspace{-2mm}

\begin{quote}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{quote}

\vspace{-2mm}

@@

>>>>

\makeatletter
\newenvironment{myquotation}
               {\list{}{\listparindent=0pt%whatever you need
                        \itemindent    \listparindent
                        \leftmargin=10pt%  whatever you need
                        \rightmargin=0pt%whatever you need
                        \topsep=0pt%%%%%  whatever you need
                        \parsep        \z@ \@plus\p@}%
                \item\relax}
               {\endlist}
\makeatother

\begin{myquotation}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{myquotation}

@@

\vspace{-5pt}
